% !TeX encoding = UTF-8
% !TeX program = pdflatex
% !BIB program = biber
%
% LNI (Lecture Notes in Informatics, Gesellschaft für Informatik) artifact paper.
% Build requires the GI LNI document class (lni.cls) and biber; see README.md.
% Modelled on the LNI setup used in publications/pub_rse_methodology (_quarto-lni.yml).
%
\documentclass[english,biblatex]{lni}

\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{url}

\addbibresource{artifact.bib}

\begin{document}

\title[RSE in the DELFI Community --- Artifact]{%
Artifact: A Reproducible Pipeline for Detecting Research Paradigms in the DELFI Community}

% LNI author interface (authblk-style): \author[affil#]{name}{email}{orcid}

\author[1]{Julian Dehne}{julian.dehne@gi.de}{0000-0001-9265-9619}
\author[2]{Fabian Lochner}{fabian.lochner@uni-oldenburg.de}{0009-0006-3157-5335}
\author[3]{Axel Wiepke}{axel.wiepke@uni-potsdam.de}{0000-0002-0555-4040}

\affil[1]{Gesellschaft für Informatik\\Politik und Wissenschaft\\
Weydingerstraße 14-16\\10178 Berlin\\Deutschland}
\affil[2]{Carl von Ossietzky Universität Oldenburg\\Digital Social Science\\
Ammerländer Heerstraße 114-118\\26129 Oldenburg \\Deutschland}
\affil[3]{University of Potsdam, An der Bahn 2, 14476 Potsdam, Germany}


\maketitle

\begin{abstract}
This artifact is a \emph{dataset publication} accompanying the DELFI~2026 paper
\emph{Research Software Engineering in the Learning Technologies: a replication
study of research paradigms in the DELFI community}. It releases the full set of
intermediate datasets behind the study --- the LLM annotation runs, the within-
and cross-model aggregated labels, the human re-annotations, the reference-study
evaluation, and the derived figures and tables --- together with the pipeline that
produces them. Every published number and figure is reproducible from the shipped
datasets alone, \emph{without} the copyrighted DELFI paper PDFs or a commercial
LLM API; the steps that consume those sources are optional, because their outputs
are themselves published as datasets. A programmatic guard enforces that no paper
full text is ever contained in the released data. We describe the released
datasets, the pipeline that regenerates them, the reproducibility guarantees, and
the constraints that motivated the design for the artifact-evaluation track.
\end{abstract}






{\small
\noindent\textbf{Resource Type:} Data set (with an accompanying software pipeline)\\
\noindent\textbf{License:} Code: MIT; Data: CC-BY-4.0\\
\noindent\textbf{Stable ID:} \href{https://doi.org/10.5281/zenodo.20681435}{DOI: 10.5281/zenodo.20681435}\\
\noindent\textbf{Repository:} \url{https://github.com/juliandehne/rse_in_delfi_artifact}
\par}

\begin{keywords}
Research Software Engineering \and Replication \and Large Language Models \and
Inter-Coder Reliability \and Reproducibility \and DELFI
\end{keywords}

\section{Introduction}
The companion study~\cite{dehne2026rseLearningTechnologies} replicates and extends
a 2017 analysis of research software paradigms across the DELFI proceedings, using
three open-weight large language models (LLMs) to annotate $n=798$ papers and
validating the result against the earlier human-coded reference study. This artifact packages the \emph{evidence and
the computation} behind those results. The central design constraint is legal: the analyzed DELFI papers are copyrighted,
so the artifact ships only derived data (labels, justifications, human
re-annotations, bibliographic metadata) and is built so the paper- and
API-dependent steps are optional while every published number and figure stays
reproducible.

\section{Artifact overview}
The primary artifact is the dataset collection under \texttt{data/} (enumerated in
the abstract). Accompanying it are a Python package (\texttt{pipeline/}:
\texttt{config}, the six steps and a full-text guard) and the management script
\texttt{run\_pipeline.py}, which regenerate those datasets and figures from one
another; every published number and figure is reproducible from the shipped
datasets alone. We target the data \emph{Available} and \emph{Reusable} badges: the
datasets are archived, openly licensed, documented with a data dictionary, and
accompanied by the code that regenerates them.

\section{The pipeline}
The pipeline has six steps (Table~\ref{tab:steps}); each step's output is a
published dataset. Steps~3, 5 and~6 regenerate their datasets from the shipped data
and run by default. Steps~1, 2 and~4 are \emph{optional}: their outputs are already
published, so they need only be re-run to rebuild those datasets from the original
paper PDFs (steps~1 and~4) or the LLM API (step~2).

\begin{table}[h]
\centering
\caption{Pipeline steps and default execution policy.}
\label{tab:steps}
\begin{tabular}{clll}
\toprule
\# & Step & Default & Requires \\
\midrule
1 & Preprocessing (PDF $\rightarrow$ text)      & \textbf{optional} & paper PDF folder \\
2 & LLM experiments                              & \textbf{optional} & SAIA/KISSKI API token \\
3 & Descriptive analysis (figures)               & runs             & shipped data \\
4 & Human re-annotation                          & \textbf{optional} & paper PDF folder (interactive) \\
5 & Label aggregation (intra + inter, ICR)       & runs             & shipped data \\
6 & Secondary analysis (paradigm biases)         & runs             & shipped data \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Data flow.} Step~1 extracts text from the PDFs; step~2 annotates each
paper with three LLMs (three runs each) via the SAIA API. Step~5a aggregates the
runs per model (majority vote) with \emph{intra}-LLM reliability; step~4 elicits a human label
where all three models disagree; step~5b aggregates across models (majority vote,
ties broken by the human label), reports \emph{inter}-LLM reliability and validates against the
2017 reference study. Steps~3 and~6 produce the figures and the bias analysis.
\texttt{run\_pipeline.py} runs the default steps; \texttt{-{}-paper-folder} enables
steps~1/4 and \texttt{-{}-run-experiments} (with a SAIA token) enables step~2.

\section{Reproducing the results}
After \texttt{pip install -r requirements.txt}, \texttt{python run\_pipeline.py}
regenerates --- from the shipped data, with no PDFs or API key --- the final
aggregated dataset ($798\times185$), the ICR tables, the paradigm distribution and
label trend figures, and the combined label bias tables. If the paper pdfs and the SAIA
token are available, the full pipeline is reproducible.

\section{Testing and AI Usage}

The pipeline was tested with the minimal setup (3 paper per model) for stability.
The data analysis was checked using whitebox testing and cross-comparison of the
jupyter notebooks and the python scripts that were generated by Claude Code.
AI was only used to generate build scripts and streamline the analysis scripts into
the nicely parametrized python pipeline and for automatic annotation of the columns.
The original paper and its accompanying data analysis was fully human-written.
Future work on this framework could include metamorphic testing and unit tests for the computations of
the reliability metrics.

\section{Data and the no-full-text guarantee}
The released data contain only labels, LLM/human justifications and bibliographic
metadata. The original annotation script dropped the \texttt{abstract},
\texttt{text} and \texttt{references} columns before persisting results ``for legal
reasons''; the artifact preserves and enforces this invariant programmatically:
\texttt{pipeline/fulltext\_guard.py} scans every shipped table and fails if a banned
full-text column is present or any cell exceeds a length threshold incompatible with
a short justification. Step~1's full-text output goes only to a \texttt{.gitignore}'d
directory.

The complete \textbf{codebook / data dictionary} is in \texttt{data/README.md}: it
documents every column (name, type, value range, allowed values, missing-value
coding), the column-name grammar, the data's provenance, and the (partially
synthetic) LLM generation method for regenerating the labels.

\section{LLM documentation}
Per the DELFI AET LLM policy, Table~\ref{tab:llms} lists the three open-weight
models used in step~2, all served through the KISSKI SAIA API. Each model was run
three times ($\mathrm{run}\_1$--$3$). All runs used identical, deterministic
inference parameters: \textbf{temperature}~$=0$, \textbf{top\_p}~$=1.0$,
\textbf{seed}~$=42$, no \textbf{stop sequences}, no explicit \textbf{max-tokens}
cap (provider default), a 300\,s request timeout, and no function/tool calling
(plain JSON-mode prompting). The models are open-weight, so a closed-weight
snapshot date does not apply; the snapshot is pinned by the version in the model
identifier, and the run dates are recorded in the result filenames. The pipeline checks the SAIA API for
the availability of the models (as they are quickly deprecated) and suggests the current version to be
added as a parameter.

\begin{table}[h]
\centering
\caption{LLM models and versions used for annotation (KISSKI SAIA API).}
\label{tab:llms}
\begin{tabular}{lll}
\toprule
Short name & Model identifier (version) & Runs \\
\midrule
mistral & \texttt{mistral-large-3-675b-instruct-2512} & 3 \\
llama   & \texttt{llama-3.1-sauerkrautlm-70b-instruct} & 3 \\
gemma   & \texttt{gemma-3-27b-it} & 3 \\
\bottomrule
\end{tabular}
\end{table}

\paragraph{Prompts.} The complete prompt --- the system prompt and the user-prompt
template with its \texttt{\{row[...]\}} placeholders --- is shipped verbatim at
\texttt{data/prompt\_templates/prompt\_template\_1.md}. The placeholders
\texttt{title}, \texttt{authors} and \texttt{year} resolve to public bibliographic
metadata; the placeholders \texttt{abstract}, \texttt{text} and \texttt{references}
resolve to the copyrighted paper content and are therefore the \emph{only} part of
a fully resolved prompt that cannot be redistributed. The substitution logic
(\texttt{pipeline/step2\_experiments.py}, \texttt{fill\_user\_prompt}) is included so
the resolved prompt can be regenerated by anyone holding the paper PDFs.

\section{FAIR preparation and targeted badges}
The artifact targets the \textbf{Available} and \textbf{Reusable} badges:
\emph{Findable/Available} via a stable archival DOI (Zenodo, from a tagged release)
and machine-readable metadata (\texttt{CITATION.cff}); \emph{Accessible} via open
licensing (MIT code, CC-BY-4.0 data; \texttt{LICENSE}, \texttt{LICENSE-data});
\emph{Interoperable} via open CSV with the documented codebook above; and
\emph{Reusable} via a parameterised, documented, re-runnable pipeline. No personal or human-subject data are released, so no further
DSGVO/ethics statement beyond the no-full-text guarantee is required.

\section{Requirements and environment}
Python~3.11+, \texttt{pandas}, \texttt{numpy}, \texttt{scikit-learn},
\texttt{krippendorff}, \texttt{statsmodels}, \texttt{matplotlib} and
\texttt{openpyxl}; see \texttt{requirements.txt}. \texttt{pymupdf} is needed only to
re-run step~1, and an OpenAI-compatible client plus a SAIA token only to re-run
step~2.

\nocite{rseInDelfiArtifact}
\printbibliography

\end{document}
